### 2014-04-15 brains-protocol.tex
Time is always discrete, either binned or sliding

\begin{itemize}
    \item \textbf{Time} can be kept continuous or made discreet (the model described above has continuous time),
    \item The \textbf{source time interval} from which a source quote is selected can span a fixed number of days, or can go back to the beginning of the quotation family,
    \item \textbf{Source quotes} in the source interval for substitutions can be further restricted, e.g. to only the most frequent quote in the interval as in the model described above,
    \item \textbf{Destination quotes} for substitutions can be further restricted, e.g. to only quotes that did not appear in the source time interval (ensuring it is the first occurrence of the destination quote).
\end{itemize}

These various flavors of an ideal substitution detection model %not only
 have an impact on whether occurrences are considered as substitutions or repetition of the original quote. %, but also essentially modify how many times a given

%variations essentially modify the balance between

%considering the second blue quote as a reproduction of the first blue because the time window is too short

%quote or as a mutation

%taking into account the possibility of a

%reproduction of previous occurrences of a quote and re-creation of itself by a new substitution instance.

@@

A discreet time is best suited to observe this: we first slice each quotation family into a number of time bags, each bag $\mathcal{B}_n$ containing all the quotations that appear in its corresponding time interval $\left[ t_n, t_{n + 1} = t_n + \Delta t \right[$ (where $\Delta t$ is a number of days, 2 in practice).
Each quote in a time bag is counted as many times as it occurs in the corresponding time interval.

>>>>

\begin{itemize}
    \item \textbf{Time} can be sliced into bins to build time bags (as in the model described above) or kept fine-grained by using sliding time bags,
    \item The \textbf{source time interval} from which a source quote is selected can span a fixed number of days, or can go back to the beginning of the quotation family,
    \item \textbf{Source quotes} in the source interval for substitutions can be further restricted, e.g. to only the most frequent quote in the interval as in the model described above,
    \item \textbf{Destination quotes} for substitutions can be further restricted, e.g. to only quotes that did not appear in the source time interval (ensuring it is the first occurrence of the destination quote).
\end{itemize}

These various flavours of an ideal substitution detection model essentially change whether occurrences are considered as substitutions from another quote or repetitions of the original quote.

@@

A discrete time is best suited to observe this: we first slice each quotation family into a number of time bags, each bag $\mathcal{B}_n$ containing all the quotations that appear in its corresponding time interval $\left[ t_n, t_{n + 1} = t_n + \Delta t \right[$ (where $\Delta t$ is a number of days, 2 in practice).
Each quote in a time bag is counted as many times as it occurs in the corresponding time interval.
